MS_data_clean

### 2021-10-15 MS_data_modeling/MS_data_explore.Rmd
Adds MS sources and pollen hosts. Cleans columns by removing author abbreviations.

```{r}
MS_data_format <- MS_data %>% mutate(interestBee = str_to_title(paste(Genus, sub(".*? ", "", Species)))) %>% 
  rename(degreeMS = 'Pollen host family #', specializationMS = 'Redefined pollen diet breadth') %>%
  select(interestBee, degreeMS, specializationMS) %>%
  filter(!is.na(degreeMS)) %>% arrange(interestBee)
```

@@

compare_df %>% filter(specialistFOWLER == 1, specializationMS  == 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5)
```

@@

compare_df %>% filter(specialistFOWLER == 0, specializationMS  != 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5)
```

## Plan: want to add pollen hosts so I can filter on pollen family. Discuss how to parse the authors out of appropriate MS column.

>>>>

```{r}
MS_data_format <- MS_data %>% mutate(interestBee = str_to_title(paste(Genus, sub(".*? ", "", Species)))) %>% 
  rename(degreeMS = 'Pollen host family #', specializationMS = 'Redefined pollen diet breadth', pollenHosts = 'Pollen hosts') %>%
  select(interestBee, pollenHosts, degreeMS, specializationMS, References) %>%
  filter(!is.na(degreeMS)) %>% arrange(interestBee) %>% mutate(pollenHosts = str_to_title(gsub("[A-Za-z]*[^A-Za-z/, ]\\S*\\s*", "", pollenHosts)))

MS_data_format
```

@@

compare_df %>% filter(specialistFOWLER == 1, specializationMS  == 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE)
```

@@

compare_df %>% filter(specialistFOWLER == 0, specializationMS  != 'Polylectic') %>% 
  select(interestBee, specializationMS, specialistFOWLER, degreeGLOBEE_C5, degreeGLOBEE) %>% filter(degreeGLOBEE_C5 > 5)
```

## Plan: want to add pollen hosts so I can filter on pollen family. Discuss how to parse the authors out of appropriate MS column. ## DONE

## Cleaning up source and pollen columns (removin author abbreviation)   ### DONE

## Create slides / tables explaining odd bees between datasets (ie. fowler specialist vs MS non-specialist and vis versa)

## Check how many GLOBI bees were cut when filtering for fowler, add them back (update previously done tables)
